Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-11-30 paper/sec-pileup.tex
more work on paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{c|c|c|c||c|c|c|c}
    \hline
    \multicolumn{8}{c}{Boosted category, $\la n_{\rm PU}\ra=80$+SK}\\
    \hline
    \hline
    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.84$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
    362  &  $1.4\cdot 10^6$     & 0.31       &  $3\cdot 10^{-4}$ &
    248     &   7250             &  2.9       & 0.034 \\
        \hline
  \end{tabular}
   $\,$\\
  \vspace{0.4cm}
  \noindent
  \begin{tabular}{c|c|c|c||c|c|c|c}
    \hline
    \multicolumn{8}{c}{Intermediate category,  $\la n_{\rm PU}\ra=80$+SK}\\
    \hline
    \hline
    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.72$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
    146  &    $9\cdot 10^5$   & 0.15        &  $2\cdot 10^{-4}$      &
  53  &  2547        & 1.1        &  0.02 \\
        \hline
  \end{tabular}
    $\,$\\
  \vspace{0.4cm}
  \noindent
  \begin{tabular}{c|c|c|c||c|c|c|c}
    \hline
    \multicolumn{8}{c}{Resolved category,  $\la n_{\rm PU}\ra=80$+SK}\\
    \hline
    \hline
    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.49$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
  1123  &    $8.5\cdot 10^6$   & 0.40       &  $1.3\cdot 10^{-4}$       &
  432  &  $3\cdot 10^4$        &   2.5      & 0.15 \\
        \hline
  \end{tabular}
  \caption{\small The results for the number of signal and
    background events
    at the HL-LHC for both the cut-based analysis and after the
    optimal MVA cut, as well as the $S/\sqrt{B}$ and $S/B$
    values in the two cases, in the case of $\la n_{\rm PU}\ra=80$
    and SK subtraction.
    %
    The corresponding results without PU were collected
    in Fig.~\ref{table:cutflowMVA}.
        \label{table:cutflowMVA_PU}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \small
  \begin{tabular}{c|c|c|c||c|c|c|c}
    \hline
    \multicolumn{8}{c}{Boosted category, $\la n_{\rm PU}\ra=80$+SK}\\
    \hline
     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.84$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
    362  &  $1.4\cdot 10^6$     & 0.31       &  $3\cdot 10^{-4}$ &
    248     &   7250             &  2.9       & 0.034 \\
    \hline
       \multicolumn{8}{c}{$\quad$}\\
    \hline
    \multicolumn{8}{c}{Intermediate category,  $\la n_{\rm PU}\ra=80$+SK}\\
    \hline
    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.72$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
    146  &    $9\cdot 10^5$   & 0.15        &  $2\cdot 10^{-4}$      &
  53  &  2547        & 1.1        &  0.02 \\
  \hline
  \multicolumn{8}{c}{$\quad$}\\
    \hline
    \multicolumn{8}{c}{Resolved category,  $\la n_{\rm PU}\ra=80$+SK}\\
    \hline
     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.49$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
  1123  &    $8.5\cdot 10^6$   & 0.40       &  $1.3\cdot 10^{-4}$       &
  432  &  $3\cdot 10^4$        &   2.5      & 0.15 \\
        \hline
  \end{tabular}
  \caption{\small Same as Table~\ref{table:cutflowMVA} in the case
    of PU+SK, with $\la n_{\rm PU}\ra=80$.
        \label{table:cutflowMVA_PU}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-30 paper/sec-results.tex
more work on paper

\subsection{Comparison with previous work}

The feasibility of Higgs pair production at the HL-LHC in different
final-state channels
has been explored various groups~\cite{Baur:2003gp,Barger:2013jfa,
  Baur:2003gpa,Barr:2013tda,Dolan:2013rja,
  Dolan:2012rv,Papaefstathiou:2012qe,Gouzevitch:2013qca,Cooper:2013kia,Wardrope:2014kya,deLima:2014dta}, though
the $4b$ final state has received less attention than other final states,
due to the complexity of disentangling the signal over the large
QCD multijet background.
%
Now we compare with two recent studies that have also studied the
feasibility of SM Higgs pair production in the $4b$ final state,
those of the UCL group~\cite{Wardrope:2014kya} and of the
Durham group~\cite{deLima:2014dta}.
%
In order to perform a meaningful comparison, we will only consider
here the $4b$ QCD and $t\bar{t}$ backgrounds, as was done
in these two studies.

First of all let us briefly summarize these two studies.
%
In the UCL group study~\cite{Wardrope:2014kya} is based
on requiring at least four $b$-tagged $R=0.4$ anti-$k_T$ jets
in the central acceptance with $p_T \ge 40$ GeV, which are
then used to form dijets (Higgs candidates) with
$p_T \ge 150$ GeV, $85 \le m_{\rm dijet} \le 140$ GeV
and $\Delta R \le 1.5$ between the two jets that form
each dijet system.
%
In addition to the basic selection cuts, a large number
of additional variables are combined using a
Boosted Decision Tree (BDT) discriminant.
%
This study considers the $b\bar{b}b\bar{b}$ and
$b\bar{b}c\bar{c}$ QCD multijets as well as
$t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$.
%
Their final significance is found to the $S/\sqrt{B}=2.1$ at the HL-LHC.

@@

  In the section section we show how Multivariate Analysis can be used
  to substantially improve the signal significance obtained in the
  cut-based analysis.

>>>>

\subsection{The role of light jet mistags}

One of the main differences of the present study as compared
to previous works is the simulation of both irreducible
and reducible background components, which allows
to study the impact of the modeling of light and charm jet mistags. 
%
Now we compare our results with two recent studies that have also studied the
feasibility of SM Higgs pair production in the $4b$ final state,
those of the UCL group~\cite{Wardrope:2014kya} and of the
Durham group~\cite{deLima:2014dta}.
%
In the UCL group study~\cite{Wardrope:2014kya} is based
on requiring at least four $b$-tagged $R=0.4$ anti-$k_T$ jets
in the central acceptance with $p_T \ge 40$ GeV, which are
then used to form dijets (Higgs candidates) with
$p_T \ge 150$ GeV, $85 \le m_{\rm dijet} \le 140$ GeV
and $\Delta R \le 1.5$ between the two jets that form
each dijet system.
%
In addition to the basic selection cuts, a large number
of additional variables are combined using a
Boosted Decision Tree (BDT) discriminant.
%
This study considers the $b\bar{b}b\bar{b}$ and
$b\bar{b}c\bar{c}$ QCD multijets as well as
$t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$.
%
Their final significance is found to the $S/\sqrt{B}=2.1$ at the HL-LHC.

@@
